Stay in Shape! A geometric algorithmic excersize collection

### 2016-02-15 geometricAlgorithms/exercisze/excersizes.tex
trying to write me some psuedocode

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsRule{*}{mps}{*}{}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{emp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{seqsplit}

\pgfplotsset{
    compat=1.9,
    compat/bar nodes=1.8
}

@@

\begin{enumerate}
	\item Fold $S$ into a binary tree where left and right is decided by Y
	coordinate of the end points,
	make sure the end points have a reference ot eachother.
	Call this new Binary tree $E_{bin}$.
\item Now Pop the top two events from $E_{bin}$
\end{enumerate}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsRule{*}{mps}{*}{}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{emp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{seqsplit}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\pgfplotsset{
    compat=1.9,
    compat/bar nodes=1.8
}

@@

\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}
